\section{Projects}

    \subsection{Personal}

        %\cventry[spacing]{years}{degree or job title}{institution or employer}{city}{grade}{description}

        \cventry
            {Summer 2017 (solo)} %year
            {Generic Lex (C++)} %project title
            {} %Instituition 
            {Bachelors} %Location
            {College of Engineering Pune} 
            {
                Basic generic lexical analyzer to define any syntax whose grammar is given by the user in the form of regular expressions.     
                \begin{itemize}
                    \item Experience in practical implementation of parsing. 
                    \item Project Link : \href{https://github.com/jaag5678/Dragon.git}{GenLex}
                \end{itemize}
            }
            {}

        \cventry
            {Summer 2016 (solo)} %year
            {Automata Generator (C++)} %project title
            {} % Course 
            {Bachelors} 
            {College of Engineering Pune} %Location
            {
                Automata generator used to define grammars in the form of regular expressions given by the user.
                Functionalities to convert from deterministic to non-deterministic automata and vice versa and verify if given input belongs to the grammar.
                \begin{itemize} % Description(s) of experience/contributions/knowledge
                    \item Experience in C++ coding, C++ templates and recursion style programming.
                    \item Project Link : \href{https://github.com/jaag5678/TCS_App.git}{AutomataGen}
                \end{itemize}
            }
            {}

        \cventry
            {Summer 2016 (solo)} %year
            {Assembler for 8086 (C)} %project title
            {} % Course 
            {Bachelors}
            {College of Engineering Pune} %Location 
            {
                A full fledged assembler for a subset of 8086. 
                \begin{itemize} % Description(s) of experience/contributions/knowledge
                    \item Experience in practical implementation of assembler pipeline.
                    \item Successfully designed assembler for 10 instructions of 8086.
                \end{itemize}
            }
            {}

    \subsection{Course-based}

        \cventry
            {Winter 2022 (solo)} %year
            {Constraint driven Scheduling of fine-grained C concurrency for Reconfigurable Hardware} %project title
            {High level Synthesis of Digital Systems} % Course 
            {PhD} 
            {McGill University} %Location
            {
                Proposed to design an optimization addressing resource constraints while synthesizing designs for concurrent hardware.
                Addresses the scheduling problem of HLS designs for fine grained concurrent constructs.
                \begin{itemize} % Description(s) of experience/contributions/knowledge
                  \item Experience in high level design specification for VHDL circuits.
                  \item Experience in using Intel Quartus hardware design tool.
                  \item Project link: \href{https://github.com/jaag5678/COMP-764---HLS/tree/master/Project}{HLS-Project}.
                \end{itemize}
            }
            {}

        \cventry
            {Winter 2020 (solo)} %year
            {Kripke Style Interpretation of lambda circle} %project title
            {MetaProgramming} % Course 
            {Masters} 
            {McGill University, Montreal} %Location
            {
                Proposed to represent the "next" temporal logic operator using Kripke Style semantics.
                \begin{itemize} % Description(s) of experience/contributions/knowledge
                    \item Experience in analyzing the corelation between modal logic and temporal logic. 
                    \item Project report link: \href{https://www.overleaf.com/read/vycfvpgbvvrp}{KripkeLambdaCircle}.
                \end{itemize}
            }
            {}

        \cventry
            {Fall 2019 (solo)} %year
            {Extending Typer with Linear Types} %project title
            {Semantics of Programming Languages} % Course 
            {Masters} 
            {University of Montreal} %Location
            {
                Proposed to extend an existing language with Linear Types.
                \begin{itemize} % Description(s) of experience/contributions/knowledge
                    \item Experience reading and implementing extension of compiler code designed in OCAML. 
                    \item Experience working with Functional programming languages. 
                    \item Project report link:\href{https://www.overleaf.com/read/vbmgfqzjkysk}{TyperExtLinearTypes}.
                \end{itemize}
            }
            {}

        \cventry
            {Winter 2019 (solo)} %year
            {Vocabulary and its Influence on Computer Science Research} %project title
            {Epistemic and Sociocultural Understanding of Computer Science} % Course 
            {Masters} 
            {McGill University} %Location
            {
                Wrote a research paper that discusses the role of vocabulary in CS research and its influence on CS education across different communities.
                \begin{itemize} % Description(s) of experience/contributions/knowledge
                    \item Experience understanding Pierre Bourdieu's work on "Reproduction in Education, Society and Culture".
                    \item Link to paper : \href{https://www.overleaf.com/read/qpnksypscjhc}{Vocabulary in CS research and its Impact}
                \end{itemize}
            }
            {}

        \cventry
            {Winter 2019 (group of 2)} %year
            {Compiler for GoLite (OCAML)} %project title
            {Compiler Construction} % Course 
            {Masters} 
            {McGill University} %Location
            {
                Designed a full fledged compiler for compiling a subset of GO language to Python.
                \begin{itemize} % Description(s) of experience/contributions/knowledge
                    \item Experience building every phase of compiler (Lexical, Parsing, Semantics and Code gen). 
                    \item Experience in using OCAML language to build a fully functional compiler.
                    \item Project Link with report: \href{https://github.com/comp520/2019_group15.git}{GoLite Compiler}.
                \end{itemize}
            }
            {}

        \cventry
            {Fall 2018 (group of 4)} %year
            {Foundations of Programming for Grade 6 students} %project title
            {Course: Teaching in Computer Science} % Course 
            {Masters} 
            {McGill University} %Location
            {
                Designed an entire course on programming foundations, including a subset of lectures, assignments and rubrics for grade 6 students. 
                \begin{itemize} % Description(s) of experience/contributions/knowledge
                    \item Experience designing syllabus catering towards first time programming students. 
                    \item Experience in teaching concepts of geometry using programming.
                \end{itemize}
            }
            {}

        \cventry
            {Fall 2018 (solo)} %year
            {Predicting Compiler Optimizations in C (bash, C, Python)} %project title
            {Machine Learning} % Course 
            {Masters} 
            {McGill University} %Location
            {
                Designed and trained a machine learning model to predict the optimal gcc compiler optimization level for a given program. %Critical insights were gained on analysis of training data and predictions.
                \begin{itemize} % Description(s) of experience/contributions/knowledge
                    \item Experience using autoencoders. 
                    \item Experience data mining for machine learning purposes. 
                    \item Project Link with report : \href{https://github.com/jaag5678/CompOptML.git}{Compiler Optimization Prediction}
                \end{itemize}
            }
            {}

        \cventry
            {2017-2018 (group of 3)} %year
            {Ontology Based Intrusion Detection System (SPARQL, Python)} %project title
            {Final Year project} % Course 
            {Bachelors} 
            {College of Engineering Pune} %Location
            {
                Proposed building an proof of concept Intrusion Detection System (IDS) for a specific application layer based Denial of Service (DoS) attacks using HTTP protocol called as SlowDos.
                \begin{itemize} % Description(s) of experience/contributions/knowledge
                    \item Experience in reading research papers, conducting exhaustive literature review and concretely defining research statement for our problem. 
                    \item Research work link : \href{https://github.com/Chromares/IDS_Ontology.git}{Ontology-based IDS}.
                \end{itemize}
            }
            {}

        \cventry
            {2016 (group of 3)} %year
            {Interactive Debugger and Interpreter for 8086 (Python)} %project title
            {Principles of Programming Languages} % Course 
            {Bachelors} 
            {College of Engineering Pune} %Location
            {
                Designed an interactive debugger for Assembly Language incorporated with GUI crafted using PyQT4 library.
                \begin{itemize} % Description(s) of experience/contributions/knowledge
                    \item Experience in debugging 20 instructions of the 8086 instruction set.
                    \item Project Link : \href{https://github.com/jaag5678/visualemu8086}{Visualemu 8086}
                \end{itemize}
            }
            {}

        \cventry
            {2015 (solo)} %year
            {Project Othello (C)} %project title
            {Data Structures} % Course 
            {Bachelors} 
            {College of Engineering Pune} %Location
            {
                Designed a turn based game Othello (Reversi) with AI opponents and GUI (using Ncurses).
                \begin{itemize} % Description(s) of experience/contributions/knowledge
                    \item Experience in first major programming project.
                    \item Experience in effective strategies in Othello integrating as an AI opponent.
                    \item Project Link : \href{https://github.com/jaag5678/Reverse-Rebirth.git}{Project Othello}.
                \end{itemize}
            }
            {}
        
    